### 2008-11-09 anal-plot.tkz.tex
Moved plot grid to separate file

% `\input{anal-plot.tkz.tex}` in your tikzpicture to use this. Parent
% picture must define `axis` and `grid` styles

\coordinate[] (O) at (0,0) {};

% cartesian coordinates
\draw [axis,->] ($ (O) - (0,1.8) $)--($ (O) + (0,0.5) $) node[label=left:$y$] {};
\draw [axis,->] (O)--($ (O) + (1.5,0) $) node[label=above:$x$] {};

% axis marks
\draw[] (0pt,-1pt) -- (0pt,1pt);
\node[label=above left:$0$] at (O) {};

\foreach \x/\xtext in {.5/\frac{1}{2}, 1}
{\begin{scope}
    \draw[xshift=\x cm,grid] (0,0)--(0,-1.65);
    \draw[xshift=\x cm] (0pt,-1pt) -- (0pt,1pt) node[above] {$\xtext$};
  \end{scope}}

\foreach \y/\ytext in {-1.5/-\frac{3}{2}, -1, -.5/-\frac{1}{2}, 0/}
{\begin{scope}
    \draw[yshift=\y cm,grid] (0,0)--(1.2,0);
    \draw[yshift=\y cm] (1pt,0pt)--(-1pt,0pt) node[left] {$\ytext$};
  \end{scope}}

### 2008-11-10 series-plot.tkz.tex
Added Maxima program to build and plot series, included plot in the paper

\begin{figure}[htb]
  \centering
  \begin{tikzpicture}[scale=3,
                      axis/.style={draw=gray,thin},
                      grid/.style={axis,dotted}]

    \input{anal-plot.tkz.tex}
    \draw plot[only marks, mark=*, mark size=.4] file{series.mac.out};
  \end{tikzpicture}
  \label{fig:series-plot}
  \caption{Сравнение точного решения \eqref{eq:anal-solution} и
    решения в виде ряда \eqref{eq:gs-solution}}
\end{figure}

### 2008-11-10 series-plot.tpl.tkz.tex
Read `n` value from keyboard in Maxima program, too.

--- 2008-11-10 series-plot.tkz.tex
@@
     \input{anal-plot.tkz.tex}
-    \draw plot[only marks, mark=*, mark size=.4] file{series.mac.out};
+
+    \draw plot[only marks, mark=*, mark size=.4] file{series-__N.mac.out};
   \end{tikzpicture}
+  \caption{Сравнение точного решения \eqref{eq:anal-solution} и
+    решения в виде ряда \eqref{eq:gs-solution} при количестве членов
+    ряда $n=__N$}
   \label{fig:series-plot}
-  \caption{Сравнение точного решения \eqref{eq:anal-solution} и
-    решения в виде ряда \eqref{eq:gs-solution}}
 \end{figure}

### 2008-11-20 anal-plot.tkz.tex
Included solution plot to `anal-plot.tkz.tex`
Using `grid` operation instead of cycles

@@
 
+% grid
+\draw[help lines, densely dashed] ($ (O) - (0,1.6) $) grid[xstep=.5,ystep=.5] ($ (O) + (1.1,0) $);
+
 % cartesian coordinates
-\draw [axis,->] ($ (O) - (0,1.8) $)--($ (O) + (0,0.5) $) node[label=left:$y$] {};
-\draw [axis,->] (O)--($ (O) + (1.5,0) $) node[label=above:$x$] {};
+\draw [help lines,->] ($ (O) - (0,1.8) $)--($ (O) + (0,0.5) $) node[label={[black]left:$y$}] {};
+\draw [help lines,->] (O)--($ (O) + (1.5,0) $) node[label={[black]above:$x$}] {};
 
@@
 {\begin{scope}
-    \draw[xshift=\x cm,grid] (0,0)--(0,-1.65);
     \draw[xshift=\x cm] (0pt,-1pt) -- (0pt,1pt) node[above] {$\xtext$};
@@
 {\begin{scope}
-    \draw[yshift=\y cm,grid] (0,0)--(1.2,0);
     \draw[yshift=\y cm] (1pt,0pt)--(-1pt,0pt) node[left] {$\ytext$};
   \end{scope}}
+
+\draw[very thick, color=gray] plot[domain=-0.1:1.1] function{sinh(-1)*cos(x)/sin(1)};

### 2008-11-23 series-plot.tpl.tkz.tex
Using `grid` operation instead of cycles
Switched to pgfplots
Rich figure captions

--- 2008-11-10 series-plot.tkz.tex
@@
+\input{axis-options.tkz}
 \begin{figure}[htb]
   \centering
-  \begin{tikzpicture}[scale=3,
-                      axis/.style={draw=gray,thin},
-                      grid/.style={axis,dotted}]
+  \begin{tikzpicture}
+    \begin{axis}
+      \input{anal-plot.tkz.tex}
+      \label{plot:anal-by-series-__N}
 
-    \input{anal-plot.tkz.tex}
-    \draw plot[only marks, mark=*, mark size=.4] file{series.mac.out};
+      \addplot[smooth, mark=*] file{series-__N.mac.out};
+      \label{plot:series-__N}
+    \end{axis}
   \end{tikzpicture}
+  \caption{Точное решение \ref{plot:anal-by-series-__N}
+    \eqref{eq:anal-solution} и решение в виде ряда
+    \ref{plot:series-__N} \eqref{eq:gs-solution} при количестве членов
+    ряда $n=__N$}
   \label{fig:series-plot}
-  \caption{Сравнение точного решения \eqref{eq:anal-solution} и
-    решения в виде ряда \eqref{eq:gs-solution}}
 \end{figure}
